\documentclass[conference]{IEEEtran}
% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\usepackage{hyperref, textcomp, url, cite}

\begin{document}
\title{Poster: Secure Multi-Party Computation as\\ a Tool for Privacy-Preserving Data Analysis}

\author{\IEEEauthorblockN{Samuel Havron
\IEEEauthorblockA{
\emph{University of Virginia}\\
\href{mailto:havron@virginia.edu}{havron@virginia.edu}\\
}
}
}
\maketitle

% IEEE POSTER REQUIREMENTS:
%Submit an abstract no longer than two pages describing the work. The abstract title should begin with the keyword "Poster:". Include all authors with contact information and institutional affiliation in your abstract.
%Your abstract should not exceed the two page limit; non-conforming submissions will not be considered for review.
%If accepted, at least one author must be registered and a final version of the poster abstract submitted by Friday, May 13, 2016.

\begin{abstract}
A \emph{Secure multi-party computation} (MPC) protocol allows two or more parties to compute a function on sensitive input data provided by each party, without revealing anything about the inputs (other than what can be inferred from the revealed output result). 
The use of MPCs as a tool for large-scale scientific data analysis can give many
researchers and social scientists the ability to work with private datasets and conduct
studies that would otherwise be difficult to do securely without revealing some
input data to one or more parties of the computation.
Using the Obliv-C language, researchers can develop their own application-specific
MPCs and quickly deploy them for use in privacy-preserving data analysis.
A demonstration of the scalability and performance of Obliv-C for scientific data analysis
and a discussion of related work highlights the utility of the language for 
researchers who have little to no experience in cryptographic protocols. 
\end{abstract}

\section{Introduction}
Many social scientists and researchers need to perform statistical analyses across 
large, distinct datasets for their work, but they are often met with difficulties in
obtaining sensitive data and computing results in a safe manner.
For instance, an education researcher may be interested in using statistical methods 
to analyze the relationship between a student's family income and the student's 
Grade Point Average for a particular school system or collection of school systems. 
Obtaining such sensitive data is often difficult to do without trusting 
one or more parties with some of the private input data.
Secure multi-party computation (MPC) is a protocol which can be used as a tool 
for carrying out large-scale scientific data analysis.

Most current implementations of MPC work by executing instructions in a \emph{data-oblivious} manner, where the control flow of the program is independent of the 
inputs provided by each party and the program executes without any 
knowledge of the cleartext data it is operating on.
This effectively creates a black box, such that semi-honest adversaries 
cannot gain addition insight about the source data, receiving only the computated results.
Several different approaches to MPCs exist, with tradeoffs in security, speed, and
involvement of each party. The most common are based on secret sharing, homomorphic
encryption, and garbled boolean circuit construction. Secret sharing, which
scatters private inputs onto multiple different servers and uses a distributed computing
protocol to safely reach a result, assumes a majority of the servers do not collude
with each other. The homomorphic encryption model generally executes computations over
encrypted data and relies on a trusted third party to reveal the final decrypted result,
without revealing any intermediary results. The garbled circuit approach allows for
a final result to be obtained without revealing any other data about any party involved.
Many researchers and social scientists require MPCs in order to analyze datasets that are 
both large and sensitive, and they often need to rely on using an underlying 
secure computation software framework to execute such protocols.
The Approach section discusses the utility of the Obliv-C language, which is based on 
the garbled circuit evaluation MPC.

\section{Approach}

Obliv-C is a programming language which allows an application developer to
quickly implement scalable, secure MPC protocols, using the language’s 
API or writing specific functionality by extending the language's existing library as
well as experimenting with the implementation of library 
protocols\cite{cryptoeprint:2015:1153}. The language is compiled and built 
on top of the standard C language, allowing for developers to 
integrate C tools and libraries with Obliv-C seamlessly.
Obliv-C implements secure MPC through optimizations of Yao's garbled circuit protocol 
for use with semi-honest adversaries. Using this language to write applications 
that can analyze large, privacy-preserving datasets 
results of building one such application for linear regression analysis 
are shown in Preliminary Results.

The goal of using Obliv-C as a framework for secure computation is to demonstrate 
its performance capabilities and ease of use to developers whom have little 
knowledge of cryptography or circuit structures, but would greatly benefit from 
using secure MPCs to carry out privacy-preserving dataset analysis (perhaps for
social science research). An example of Obliv-C code which calculates and 
reveals results of a linear regression are seen in Figure 1.
\begin{figure}[!t]
\centering
\begin{verbatim}
obliv int orsqr = f_div(osqr(ocv),ostdvs);
revealOblivInt(&io -> rsqr,orsqr,0);
revealOblivInt(&io -> m,om,0);
revealOblivInt(&io -> b,ob,0);
\end{verbatim}
\caption{Code snippet showing \emph{obliv} qualifier and reveal API. Revealing an integer
stores the result into a struct which is accessible to specified parties.}
\label{snippet}
\end{figure}

\section{Preliminary Results}
\subsection{Scalability}
A linear regression data analysis program was developed to test the scalability 
and speed of Obliv-C as a tool for implementing MPC programs. 
Testing was done using c4.large \emph{Elastic Compute Cloud} (EC2) nodes from \emph{Amazon Web Services} (AWS)\cite{aws:ec2}, which feature 
high frequency Intel Xeon E5-2666 v3 (Haswell) processors optimized specifically for EC2,
two vCPUs, and 3.75 GiB of DRAM.
Two c4.large instances were launched and connected through 
Obliv-C's API for TCP/IP connections via Oblivious Transfer protocol. The instances 
were both located in the same cloud cluster in Oregon; exploring network latency 
impositions with secure MPCs is also an area of interest.

One node instance provided independent ($x$) data points, while the other provided 
dependent ($y$) data points; data points used were 32-bit integers, using fixed-point 
mathematics to convert raw data values into scaled integers, as 
Obliv-C does not currently support floating point numbers.
The time needed to execute the MPC between instances appears to scale linearly 
with the size of the data input; 100K data points finished execution in 12.7 minutes 
on average, 500K completed in 63.7 minutes, and 1 million data points finished execution 
in just over 127 minutes on average. Given the relative cost of using a c4.large instance
(as of writing, \$0.105 per hour), executing this program over larger inputs, such as
10 million data points, will only incur about \$4.45 between two instances in the 
estimated runtime of 21 hours.

Artificial data was generated for testing the scalability of input size, and
considerations to automated data match-ups between two separate datasets were not
implemented; the artifical data was presumed to already be matched and sorted properly.
To provide a clear example of the utility of Obliv-C for analyzing sensitive datasets, 
additional data for computation was obtained from the public New York State Department 
of Health dataset of Hospital Inpatient Discharges from 2011\cite{healthdata:ny}. 
Comparisons between fields such as "Length of Days stayed" and "Total Costs" 
over approximately 2.6 million data points are currently being tested.
This dataset is particularly amenable to analysis, as all data is already 
matched properly and each data value is a comparable number.

\subsection{Discussion}
All numbers are averages over 5 executions between c4.large instances. The datasets used in Preliminary Results assume that data is matched, sorted, and 
comprises of comparable values. Using private set intersection to assist matching 
data with a unique identifier and automatically filtering out incompatible 
data points is considered for future work.

\section{Related Work}
A similar approach in taking distinct federal datasets and comparing them is seen in
Dan Bogdanov \emph{et al.}, where correlations between working hours and failure to
graduate on time in Estonia was investigated, matching over 10 million 
tax records and 500K education records\cite{cryptoeprint:2015:1159}.
This analysis utilized the researchers' own framework for secure
computation, \emph{ShareMind}, a database and analytics system which 
almost exclusively uses three-parties to carry out computations, and uses arithmetic
manipulations to implement secure MPC, rather than boolean circuit evaluation\cite{sharemind}.

Another privacy-preserving approach to analyzing millions of records uses a
combination of homomorphic encryption (for linear computations) and Yao circuits 
(for non-linear computations) in order to compute ridge regression\cite{ridgeregression}.
This approach is designed for many users to send data to a central server called the 
\emph{Evaluator}, in contrast to the primarily two-party model presented in the Obliv-C
language. Yet another approach used for secure multiple linear regression 
relies on protocols based on homomorphic secret sharing, and data which is partitioned 
across several databases\cite{secretsharing}.
 
\section{Conclusion}
Using MPCs for scientific analysis of large datasets is promising for social scientists
and researchers whom would otherwise need to reveal some of one party's input to another
party in order to analyze their data. 
The Obliv-C language is particularly well-suited for implementing such scalable, 
sensitive data analysis between two or more parties, and shows the practicality of 
using secure MPCs for processing large datasets.
Future work invites a closer examination of automatic data-matching between
separate datasets with private set intersection, improving fixed-point integer 
conversion for decimal data values used in computation, and other privacy-preserving
applications.

% references section
\begin{thebibliography}{1}

\bibitem{aws:ec2}
  \url{https://aws.amazon.com/ec2/instance-types/}.

\bibitem{healthdata:ny}
  \url{https://health.data.ny.gov/}.

\bibitem{sharemind}
Dan Bogdanov, S. Laur, and J. Willemson,
\emph{Sharemind: A framework for fast privacypreserving
computations}, In 13th European Symposium on Research in Computer
Security (ESORICS), volume 5283 of LNCS, pages 192–206. Springer, 2008.
\url{http://sharemind.cyber.ee}.

\bibitem{cryptoeprint:2015:1159}
    Dan Bogdanov, Liina Kamm, Baldur Kubo, Reimo Rebane, Ville Sokk, Riivo Talviste,
    \emph{Students and Taxes: a Privacy-Preserving Social Study Using Secure Computation},
    Cryptology ePrint Archive, Report 2015/1159,
    2015,
    \url{http://eprint.iacr.org/}.

\bibitem{secretsharing}
  Rob Hall, Stephen E. Fienberg, and Yuval Nardi, 
  \emph{Secure multiple linear regression based on homomorphic encryption}, 
  J. Official Statistics, vol. 27, no. 4, 2011.

\bibitem{ridgeregression}
 Valeria Nikolaenko, Udi Weinsberg, Stratis Ioannidis, Marc Joye, Dan Boneh, Nina Taft,
 \emph{Privacy-Preserving Ridge Regression on Hundreds of Millions of Records},
 in 2013 IEEE Symposium on Security and Privacy (S\&P 2013), pp. 334-348, 
 IEEE Computer Society, 2013,
 \url{http://www.technicolorbayarea.com/papers/2013/NWIJBT13garbled.pdf}.

\bibitem{cryptoeprint:2015:1153}
  Samee Zahur and David Evans, \emph{Obliv-C: A Language for Extensible 
  Data-Oblivious Computation}, Cryptology ePrint Archive, 
  Report 2015/1153, 2015, 
  \url{http://eprint.iacr.org/}.

\end{thebibliography}
\end{document}
